---
title: "Industrial Accidents"
author: "Narendran Ramakrishnan"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ***Project Title***: Industrial Labor Accidents
## **Source**: Kaggle dataset
## ***INTRODUCTION :***
Labor death is a very common issue in industrial field. The following dataset shows the death in different deaths in different regions in different countries.
The different variables present in the data set is shown below:
```{r, echo=FALSE}
inddeath = read.csv("C:\\Users\\Lenovo\\Desktop\\industrydeath.csv")
inddeath = inddeath[, 1:10]
colnames(inddeath)
head(inddeath)
```
Now we describe the variables above:
*X*: It is the index of the given dataset
*Data*: The dates of accidents
*Countries*: Countries where the accident occured
*Local*: The locality where accident occured
*Industry.Sector*:The industry type where the accident occured
*Accident.Level*: The level of accident occured
*Potential.Accident.Level* : Estimated level of accident
*Genre*: Gender of the victim
*Employee.or.Third.Party*: Victim's organisation status
*Critical risk*: Condition of the victim

## Plots and Graphs:

### *Accidents in countries*:

```{r, echo=FALSE}
library(ggplot2)
ggplot(inddeath,aes(x= Countries, fill = Local))+geom_bar(color = "white", width = 1)
```

### *Accidents in localities with respect to Gender*:

```{r,echo =FALSE}
ggplot(inddeath,aes(x= Local, fill = Genre))+geom_bar(color = "white", width = 1)
```

### *Accidents in localities with respect to industry* :
```{r, echo =FALSE}
ggplot(inddeath,aes(x= Local, fill = Industry.Sector))+geom_bar(color = "white", width = 1)
```

### *Accident level vs Potential accident level*:
```{r,echo = FALSE}
ggplot(inddeath, aes(x=Potential.Accident.Level, y= Accident.Level)) +
  geom_point(shape=8, size= 5, color="blue")
```
###*Critical Risk along with victim status*:

```{r,echo=FALSE}
ggplot(inddeath,aes(x= Critical.Risk, fill = Employee.or.Third.Party))+geom_bar(color = "white", width = 1)+ theme(axis.text=element_text(size=5))+coord_flip()
```